Msc Thesis Figures

### 2020-08-15 docs/msc_thesis_figures.Rmd
add summary vals

  # Ttransform, give names
  the_stack[original == 1] <- 0
  final[original == 1] <- 0
  the_stack[stratum==0] <- NA
  final[stratum==0] <- NA
  the_stack <- trim(the_stack)
  final <- trim(final)

@@

<!--
```{r eval=FALSE, include=FALSE}

# Analyze
options(yardstick.event_first = T)
crosstab(the_mean>0, final)

@@

aucs <- c()
precs <- c()
for (x in 1:nlayers(the_stack)){
the_df <- as.data.frame(stack(the_stack[[x]], final)) %>% 
drop_na() %>% 
rename(estimate = starts_with("model"), truth = "observation")
the_df_2 <- the_df %>% 
mutate(truth = factor(truth, ordered = F)) %>%
mutate(truth = relevel(.$truth, "1"))
auc <- the_df_2 %>% 
roc_auc(truth = truth, estimate) %>% 
pull(.estimate)
prec <- the_df_2 %>% 
average_precision(truth = truth, estimate) %>% 
pull(.estimate)
aucs <- c(aucs, auc)
precs <- c(precs, prec)
}
mean(aucs);sd(aucs)
mean(precs);sd(precs)
```
-->

>>>>

  # Transform, give names
  the_stack[original == 1] <- 0
  final[original == 1] <- 0
  the_stack[stratum==0] <- NA
  final[stratum==0] <- NA
  the_stack <- trim(the_stack)
  final <- trim(final)

@@

Compute auc / precision on predictions.

```{r eval=FALSE, include=FALSE}

options(yardstick.event_first = T)
# crosstab(the_mean>0, final)

summary_vals <- data.frame()

  # Transform, give names
  the_stack[original == 1] <- 0
  final[original == 1] <- 0
  the_stack[stratum==0] <- NA
  final[stratum==0] <- NA
  the_stack <- trim(the_stack)
  final <- trim(final)

@@

  aucs <- c()
  precs <- c()
  for (x in 1:nlayers(the_stack)){
    the_df <- as.data.frame(stack(the_stack[[x]], final)) %>% 
      drop_na() %>% 
      rename(estimate = starts_with("model"), truth = "observation")
    the_df_2 <- the_df %>% 
      mutate(truth = factor(truth, ordered = F)) %>%
      mutate(truth = relevel(.$truth, "1"))
    auc <- the_df_2 %>% 
      roc_auc(truth = truth, estimate) %>% 
      pull(.estimate)
    prec <- the_df_2 %>% 
      average_precision(truth = truth, estimate) %>% 
      pull(.estimate)
    aucs <- c(aucs, auc)
    precs <- c(precs, prec)
  }

  summary_vals <- bind_rows(summary_vals, 
                            data.frame(class = class, 
                                       mean_auc = mean(aucs), sd_auc = sd(aucs), 
                                       mean_prec = mean(precs), sd_prec = sd(precs)))

}

write_csv(summary_vals, "../outputs/metrics/summary_vals.csv")
summary_vals
```
